### 2012-02-12 exam3/1.tex
Touch ups to set problem.

\begin{verbatim}
;; empty-set is a set

;; A Set implements:
;; - insert : String -> Set
;; adds the given string to the set, if it isn't already there
;; - remove : String -> Set
;; removes the given string from the set
;; if the given string is not in the set, produce the original set
;; - size : -> Number
;; count the elements of the set
;; - has : String -> Boolean
;; is the given String in the set?
\end{verbatim}
\noindent
\verb|Set|s should satisfy the following property, called the
``insert-size'' property, for any element and
set:

\begin{quote}
If we insert an element into a set, then the resulting set is the
same size as the original set \emph{if} the element was already in the
set, and the resulting set is one larger than the original set
if the element was \emph{not} already in the set.
\end{quote}

@@

\noindent
The College wants to be really sure that their sets are correct, and
they've come up with another property that they think is true, called
the ``insert-remove'' property:

\begin{quote}
If we insert element $a$ into a set, and then remove element $b$ from
the resulting set, the result has the same size as if we do the two
operations in the reverse order.
\end{quote}

@@

>>>>

\begin{verbatim}
;; empty-set is a Set value containing no elements

;; A Set implements:
;; - insert : String -> Set
;;   adds given string to this set, if it isn't already there
;;   (otherwise does nothing)
;; - remove : String -> Set
;;   removes given string from this set, if it's already there
;;   (otherwise does nothing)
;; - size : -> Number
;;   count the elements of this set
;; - has? : String -> Boolean
;;   is the given String in this set?
\end{verbatim}
\noindent
\verb|Set|s should satisfy the following property, called the
``insert-size'' property, for any element and
set:

\begin{quote}
If we insert any element into any set, then the resulting set is the
same size as the original set \emph{if} the element was already in the
set, and the resulting set is one larger than the original set
if the element was \emph{not} already in the set.
\end{quote}

@@

\newpage
\ifrubric\else
[Here is some more space for the previous problem.]

\newpage
\noindent
The College wants to be really sure that their sets are correct, and
they've come up with another property that they think is true, called
the ``insert-remove'' property:

\begin{quote}
If we insert element any element $a$ into any set, and then remove any
element $b$ from the resulting set, the result has the same size as if
we do the two operations in the reverse order, i.e., remove $b$, then
insert $a$.
\end{quote}

@@

\newpage
[Here is some more space for the previous problem.]
\newpage
\fi
